\tealeaves: an R package for modelling leaf temperature using energy budgets

### 2019-07-26 ms/ms.tex
fixed style for publication

\begin{figure}[t!]
\caption{The leaf energy budget model in \tealeaves~takes environmental and leaf parameters to find the equilibrium leaf temperature ($T_\mathrm{leaf}$) at which incoming energy exactly matches outgoing energy. Under typical daytime conditions, this means thermal infrared radiation losses, sensible heat loss, and latent heat loss must balance absorbed radiation. A. The components of leaf energy budgets (thin orange lines) vary with leaf temperature (\textit{x}-axis). $T_\mathrm{leaf}$ is where the net energy flux (thick blue line) is 0 (blue point; see Eqn 1). B. 1) Radiation is emitted from sunlight and surrounding objects is absorbed by the leaf. 2) The leaf radiates some energy. 3) Heat is lost through convection when the leaf temperature is greater than air temperature. 4) Latent heat is lost through evaporation, which is driven by the vapor pressure deficit between the air and leaf interior and the leaf conductance to water vapor. Calculations used the following leaf parameter values in this example: $d = 0.1$ m; $\alpha_\mathrm{s} = 0.5$; $\alpha_\mathrm{l} = 0.97$; $g_\mathrm{sw} = 5~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $g_\mathrm{uw} = 0.1~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $\mathit{SR} = 0.5$. Calculations used the following environmental parameter values in this example: $P = 101.3246$ kPa; $r = 0.2$; $\mathit{RH} = 0.5$; $S_\mathrm{sw} = 1000$ W m$^{-2}$; $T_\mathrm{air} = 298.15$ K; $u = 2$ m s$^{-1}$. See Table \ref{table:table_input} for symbol definitions.}
\label{fig:fig1}
\end{figure}

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $d$ & 0.1 & 0.004 -- 0.4 m & \cite{Wright_etal_2017} \\
  $\alpha_\mathrm{l}$ & 0.97 & 0.95 -- 0.97 & \cite{Gutschick_2016} \\
  $\alpha_\mathrm{s}$ & 0.5 & 0.4 -- 0.6 & \cite{Jones_2014} \\
  $g_\mathrm{sw}$ & 5 & 0.01 -- 10 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ & \cite{Lin_etal_2015, Duursma_etal_2019} \\
  $g_\mathrm{uw}$ & 0.1 & 0.01 -- 1 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ & \cite{Duursma_etal_2019} \\
  $\mathit{SR}$ & 0.5 & 0 -- 1 (untransformed) & \cite{Muir_2015} \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $P$ & 101.3246 & 50 (5000 mas$^\dagger$) -- 100 (0 mas) kPa & \cite{Korner_2007, Stull_2011} \\
  $r$ & 0.2 & 0.1 (lava) -- 0.6 (ice) & \cite{Stull_2011} \\
  $\mathit{RH}$ & 0.5 & 0 -- 1 & \cite{Jones_2014} \\
  $S_\mathrm{sw}$ & 1000 & 0 -- 1000 W m$^{-2}$ & \cite{Jones_2014} \\
  $T_\mathrm{air}$ & 298.15 & 270 -- 320 K & \cite{Jones_2014} \\
  $u$ & 2 & 0 -- 10 m s$^{-1}$ & \cite{Vogel_2009} \\

@@

\begin{figure}[t!]
\caption{The effect of key leaf (\textbf{A -- C}) and environmental (\textbf{D -- F}) parameters on leaf temperature, holding other parameters constant. \textbf{A}) Greater stomatal conductance ($g_\mathrm{sw}$, \textit{x}-axis) reduces leaf temperature through latent heat loss. \textbf{B}) Larger leaves ($d$, \textit{x}-axis) have thicker boundary layers, causing them to heat up more in the sun. \textbf{C}) Amphistomatous leaves ($\mathit{SR} = 0.5$, \textit{x}-axis) lose more water through transpiration than leaves with all stomata on one surface, leading to a lower leaf temperature. \textbf{D}) Greater humidity ($\mathit{RH}$, \textit{x}-axis) increases leaf temperature by limiting latent heat loss. \textbf{E}) With low solar radiation ($S_\mathrm{sw}$, \textit{x}-axis), leaf temperature is below air temperature; with high solar radiation, leaf temperature is greater than air temperature. \textbf{F}) At greater wind speeds ($u$, \textit{x}-axis) leaf temperature is more closely coupled to air temperature. The discontinuity represents the shift from laminar to turbulent flow. For reference, the dashed line is the air temperature in all simulations. All calculations used the following leaf parameter values unless they varied: $d = 0.1$ m; $\alpha_\mathrm{s} = 0.5$; $\alpha_\mathrm{l} = 0.97$; $g_\mathrm{sw} = 5~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $g_\mathrm{uw} = 0.1~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $\mathit{SR} = 0.5$. All calculations used the following environmental parameter values unless they varied: $P = 101.3246$ kPa; $r = 0.2$; $\mathit{RH} = 0.5$; $S_\mathrm{sw} = 1000$ W m$^{-2}$; $T_\mathrm{air} = 298.15$ K; $u = 2$ m s$^{-1}$. See Table \ref{table:table_input} for symbol definitions.}
\label{fig:figS1}
\end{figure}

>>>>

\begin{figure}[t!]
\caption{The leaf energy budget model in \tealeaves~takes environmental and leaf parameters to find the equilibrium leaf temperature ($T_\mathrm{leaf}$) at which incoming energy exactly matches outgoing energy. Under typical daytime conditions, this means thermal infrared radiation losses, sensible heat loss, and latent heat loss must balance absorbed radiation. A. The components of leaf energy budgets (thin orange lines) vary with leaf temperature (\textit{x}-axis). $T_\mathrm{leaf}$ is where the net energy flux (thick blue line) is 0 (blue point; see Eqn 1). B. 1) Radiation is emitted from sunlight and surrounding objects is absorbed by the leaf. 2) The leaf radiates some energy. 3) Heat is lost through convection when the leaf temperature is greater than air temperature. 4) Latent heat is lost through evaporation, which is driven by the vapor pressure deficit between the air and leaf interior and the leaf conductance to water vapor. Calculations used the following leaf parameter values in this example: $d = 0.1$ m; $\alpha_\mathrm{s} = 0.5$; $\alpha_\mathrm{l} = 0.97$; $g_\mathrm{sw} = 5~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $g_\mathrm{uw} = 0.1~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $\mathrm{SR} = 0.5$. Calculations used the following environmental parameter values in this example: $P = 101.3246$ kPa; $r = 0.2$; $\mathrm{RH} = 0.5$; $S_\mathrm{sw} = 1000$ W m$^{-2}$; $T_\mathrm{air} = 298.15$ K; $u = 2$ m s$^{-1}$. See Table \ref{table:table_input} for symbol definitions.}
\label{fig:fig1}
\end{figure}

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $d$ & 0.1 & 0.004 -- 0.4 m & \cite{Wright_etal_2017} \\
  $\alpha_\mathrm{l}$ & 0.97 & 0.95 -- 0.97 & \cite{Gutschick_2016} \\
  $\alpha_\mathrm{s}$ & 0.5 & 0.4 -- 0.6 & \cite{Jones_2014} \\
  $g_\mathrm{sw}$ & 5 & 0.01 -- 10 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ & \cite{Lin_etal_2015, Duursma_etal_2019} \\
  $g_\mathrm{uw}$ & 0.1 & 0.01 -- 1 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ & \cite{Duursma_etal_2019} \\
  $\mathrm{SR}$ & 0.5 & 0 -- 1 (untransformed) & \cite{Muir_2015} \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $P$ & 101.3246 & 50 (5000 mas$^\dagger$) -- 100 (0 mas) kPa & \cite{Korner_2007, Stull_2011} \\
  $r$ & 0.2 & 0.1 (lava) -- 0.6 (ice) & \cite{Stull_2011} \\
  $\mathrm{RH}$ & 0.5 & 0 -- 1 & \cite{Jones_2014} \\
  $S_\mathrm{sw}$ & 1000 & 0 -- 1000 W m$^{-2}$ & \cite{Jones_2014} \\
  $T_\mathrm{air}$ & 298.15 & 270 -- 320 K & \cite{Jones_2014} \\
  $u$ & 2 & 0 -- 10 m s$^{-1}$ & \cite{Vogel_2009} \\

@@

\begin{figure}[t!]
\caption{The effect of key leaf (\textbf{A -- C}) and environmental (\textbf{D -- F}) parameters on leaf temperature, holding other parameters constant. \textbf{A}) Greater stomatal conductance ($g_\mathrm{sw}$, \textit{x}-axis) reduces leaf temperature through latent heat loss. \textbf{B}) Larger leaves ($d$, \textit{x}-axis) have thicker boundary layers, causing them to heat up more in the sun. \textbf{C}) Amphistomatous leaves ($\mathrm{SR} = 0.5$, \textit{x}-axis) lose more water through transpiration than leaves with all stomata on one surface, leading to a lower leaf temperature. \textbf{D}) Greater humidity ($\mathrm{RH}$, \textit{x}-axis) increases leaf temperature by limiting latent heat loss. \textbf{E}) With low solar radiation ($S_\mathrm{sw}$, \textit{x}-axis), leaf temperature is below air temperature; with high solar radiation, leaf temperature is greater than air temperature. \textbf{F}) At greater wind speeds ($u$, \textit{x}-axis) leaf temperature is more closely coupled to air temperature. The discontinuity represents the shift from laminar to turbulent flow. For reference, the dashed line is the air temperature in all simulations. All calculations used the following leaf parameter values unless they varied: $d = 0.1$ m; $\alpha_\mathrm{s} = 0.5$; $\alpha_\mathrm{l} = 0.97$; $g_\mathrm{sw} = 5~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $g_\mathrm{uw} = 0.1~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $\mathrm{SR} = 0.5$. All calculations used the following environmental parameter values unless they varied: $P = 101.3246$ kPa; $r = 0.2$; $\mathrm{RH} = 0.5$; $S_\mathrm{sw} = 1000$ W m$^{-2}$; $T_\mathrm{air} = 298.15$ K; $u = 2$ m s$^{-1}$. See Table \ref{table:table_input} for symbol definitions.}
\label{fig:figS1}
\end{figure}
